### 2014-02-18 latex-template/example.tex
feat(template): add iitsrc template

\documentclass{iitsrc}
\usepackage{graphicx}
\usepackage{mflogo}
\usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
%\PrerenderUnicode{áäčďéíľĺňóôŕšťúýžÁÄČĎÉÍĽĹŇÓÔŔŠŤÚÝŽ}

% Please do not remove the following commands:
\editpages{1}{8}

\title{Guidelines for Authors of Papers Published\\~in Proceedings of IIT.SRC 2014}
\titlerunning{Guidelines for Authors of Papers Published in Proceedings of IIT.SRC 2014}
\author{Ján}{Novák}
\author{Martin}{Kováč}
\supervision{\bc~/~\ms~/~\phd}
            {\info~/~\compeng~/~\softeng~/~\infosys~/~\appinf}
            {Professor~/~Assoc.~Professor~/~Dr.~Xxxx Yyyyy}
            {\iai~/~\iise~/~\icsn, \fiit}
\mail{novak@fiit.stuba.sk}
\field{To Be Added by Editor}

\begin{document}

\begin{abstract}
All IIT.SRC \LaTeX{} contributions are expected to use the {\tt iitsrc}
class. This document was typeset with that class and as such it is
solely a demo. It is a supplement to the {\tt iitsrc.pdf} document which
describes all the (boring) things in detail.\footnotemark
\end{abstract}

\section{Basics}
%
\footnotetext{Abstract should be no longer than 100 words.}
%
We do not hope to give you as extensive information as other sources (such
as~\cite{lamport:latex}). On Linux you can get fairly complete
information about \LaTeX{} commands via:

\begin{verbatim}
    info latex
\end{verbatim}
Here we only make few notes concerning obvious things you probably
already know.
%
You should properly divide your text into several sections (via
\verb|\section| and perhaps also \verb|\subsection| commands.)
%
Do not change the font family and font sizes defined by the
\verb|iitsrc| class. These default values should be common for all
articles.
%
If you want to emphasize something (perhaps a newly introduced notion
or such), use the \verb|\em| command.
%
Usage of the bold face (the \verb|\bf| command) is very unusual in
normal \LaTeX{} text. It is not advised to use it explicitly.
%
End of a paragraph is indicated in the source code by an empty line.
%
You can use usual environments such as \verb|itemize| or
\verb|enumerate| to create bulleted or enumerated lists.
%
\section{Mathematical formul\ae, equations, figures and tables}
%
The \verb|equation| environment can be used for typesetting numbered
equations.
\begin{equation}
\label{eq:contestwinner}
e^{i\pi}+1=0
\end{equation}
It was produced with a following commands:
\begin{verbatim}
   \begin{equation}
   e^{i\pi}+1=0
   \end{equation}
\end{verbatim}
If you want later to refer to your equation, it is wise to accompany
your equation with a symbolic label, for example as below:
\begin{verbatim}
   \begin{equation}
   \label{eq:contestwinner}
   e^{i\pi}+1=0
   \end{equation}
\end{verbatim}
Now you can refer to it---the
Equation~\ref{eq:contestwinner}---by its
symbolical name rather than a concrete number. This is advantageous
because the order of equations might change over time. This reference
can be typeset as follows:
\begin{verbatim}
   Equation~\ref{eq:contestwinner}
\end{verbatim}
There is also \verb|equation*| environment which enables you to
typeset unnumbered equation.

There are also other useful \LaTeX{} commands and environments such as
\verb|eqnarray|. For example:
\begin{eqnarray}
x & \ll  & y_1 + \cdots + y_n\\
x & \leq & z
\end{eqnarray}
It enables you to put (non-)equalities nicely one below the other
pleasantly aligned. The above example was typeset by a following
command:
\begin{verbatim}
   \begin{eqnarray}
   x & \ll  & y_1 + \cdots + y_n\\
   x & \leq & z
   \end{eqnarray}
\end{verbatim}
%
If you need to typeset a table such as Table~\ref{tab:strategy}
\begin{table}[ht]
    \caption{Specification of a strategy  $s(a)$ of agent $a$.}
    \label{tab:strategy}
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
        \hline
        & penalty & penalty & movement\\
        & of agent $a$ & of agent $b$ & of agent $a$\\
        \hline
        1 & $p(a)=0$ & $p(b)=0$ & $S_1(a)$\\
        2 & $p(a)=0$ & $p(b)>0$ & $S_2(a)$\\
        3 & $p(a)>0$ & $p(b)=0$ & $S_3(a)$\\
        4 & $p(a)>0$ & $p(b)>0$ & $S_4(a)$\\
        \hline
    \end{tabular}
\end{center}
\end{table}
you can do it as follows:
\begin{verbatim}
    \begin{table}[ht]
        \caption{Specification of a strategy
                 $s(a)$ of agent $a$.}
        \label{tab:strategy}
        \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            & penalty & penalty & movement\\
            & of agent a & of agent b & of agent a\\
            \hline
            1 & $p(a)=0$ & $p(b)=0$ & $S_1(a)$\\
            2 & $p(a)=0$ & $p(b)>0$ & $S_2(a)$\\
            3 & $p(a)>0$ & $p(b)=0$ & $S_3(a)$\\
            4 & $p(a)>0$ & $p(b)>0$ & $S_4(a)$\\
            \hline
        \end{tabular}
    \end{table}
\end{verbatim}
%
If you need to include a figure to your document,
such as Figure~\ref{fig:fractaltree},
\begin{figure}[t]
    \begin{center}
        \includegraphics{tree}
        \caption{Fractal tree.}
        \label{fig:fractaltree}
    \end{center}
\end{figure}
you can do it as follows:
\begin{verbatim}
    \begin{figure}[h]
        \begin{center}
            \includegraphics{tree}
            \caption{Fractal tree}
            \label{fig:fractaltree}
       \end{center}
   \end{figure}
\end{verbatim}
If you process your document with \LaTeX\ you will have to
provide all your figures as EPS (Encapsulated Postscript) files.
If you process your document with PDF\LaTeX\ you will have to
provide all your figures as PDF files. Several graphical programs
are able to export pictures to these two formats.
If possible, please use a
vector editor. Please do not convert bitmaps into EPS or PDF.
The printed results are then usually ugly.

Note that since you have given a figure a symbolic name (in this case
\verb|fig:fractaltree|), you can refer to this figure as follows:
\begin{verbatim}
   Figure~\ref{fig:fractaltree}
\end{verbatim}
This is advantageous because regardless of the fact how you reorder
your figures in the document, the references to them will never
break unless you change their symbolical name.
%
Do not forget to describe your figure with a \verb|\caption| command.
%
Due to technological constraints, included figures should be
\begin{itemize}
\item black-and-white,
\item minimal thickness of lines should be at least 0.25 mm,
\item do not use half-tones; use raster instead to express various
degrees of gray.
\end{itemize}
%
If you need to insert a pseudo code of an algorithm into the
paper, you can use the algorithms package for \LaTeX.
Documentation and example in \TeX{} file can be found in the zip
file available on
\verb|http://texcatalogue.sarovar.org/entries/algorithms.html|
%
Please do not refer to various parts
of your document via page numbers. Instead, give a symbolic name
to your sections (via \verb|\label| command) and refer to your
sections via \verb|\ref| command.
%
Please leave the \verb|\editpages| command from a ``minimal article
source code'' in place. Its
purpose is related to combining particular articles to a single volume
and if you delete it, someone will have later add it back. So if you
leave it where it is, you will save yours someone else's time.
%
\section{The bibliography}
%

\def\BibTeX{{\rmfamily B\kern-.05em%
    \textsc{i\kern-.025em b}\kern-.08em%
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\LaTeX{} document usually creates bibliography references via \BibTeX.
Basic information about \BibTeX{} is in~\cite{lamport:latex}. You are
encouraged to use it too. Bibliography references are usually inserted
in the document as follows:
\begin{verbatim}
   \bibliography{common}
   \bibliographystyle{iitsrc}
\end{verbatim}
Be sure to use the \verb|iitsrc| style as suggested above. We used \BibTeX{}
also for typesetting bibliographic references cited within this
document. So you can look at the source code ({\tt demo.tex}) and the
compilation instructions ({\tt Makefile}) to see how it was
generated. The {\tt common.bib} file contains the bibligraphy resources
we collected over time. There are various entries in the form:
\begin{verbatim}
    @ARTICLE{OwickiGries76b,
        AUTHOR = {S. Owicki and D. Gries},
        TITLE = "Verifying Properties of Parallel Programs,
                 an axiomatic approach",
        JOURNAL = cacm,
        VOLUME = 19,
        NUMBER = 5,
        PAGES = {279-285},
        MONTH = may,
        YEAR = 1976
    }
\end{verbatim}
Each such entry contains logical information about the particular source
of information. You can add your sources of information therein. Some
information about how to do that can be found in~\cite{lamport:latex}
(Appendix B).  \BibTeX{} finds out which ones you cite within your
document and format the data it finds in your {\tt *.bib} (in this case
{\tt common.bib}) file according to the instructions in the {\tt *.bst}
(in this case {\tt iitsrc.bst}) file. All you have to do within your
document is to \verb|\cite{key}| them.

Other example citated
sources:~\cite{CHS03RR,friedman:switching,henessy:computer,henrio:thesis,MannaPnueli82,MisraChandy,OwickiGries76b,vardhan98distributed,WidomPanangaden,C99-draft,czarnecki:generative-programming,SWIG,leiserson:network}

\begin{itemize}
\item Item
    \begin{itemize}
    \item Item
        \begin{itemize}
        \item Item

        \end{itemize}
    \end{itemize}
\end{itemize}

\begin{enumerate}
\item Item
    \begin{enumerate}
    \item Item
        \begin{enumerate}
        \item Item

        \end{enumerate}
    \end{enumerate}
\end{enumerate}

\acknowledgement{Here you should mention the names of grants
                 which funded the work on this article. As defined
                 by the particular grant.}

\bibliography{common}
\bibliographystyle{iitsrc}
\end{document}

### 2014-02-18 latex-template/extended-abstract.tex
feat(template): add iitsrc template

--- 2014-02-18 latex-template/example.tex
@@
 \documentclass{iitsrc}
-\usepackage{graphicx}
-\usepackage{mflogo}
-\usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
-%\PrerenderUnicode{áäčďéíľĺňóôŕšťúýžÁÄČĎÉÍĽĹŇÓÔŔŠŤÚÝŽ}
+\usepackage[utf8]{inputenc}
 
-% Please do not remove the following commands:
+% Please do not remove the following command:
 \editpages{1}{8}
 
-\title{Guidelines for Authors of Papers Published\\~in Proceedings of IIT.SRC 2014}
+\title{Guidelines for Authors of Extended Abstracts\\Published in Proceedings of IIT.SRC 2014}
 \titlerunning{Guidelines for Authors of Papers Published in Proceedings of IIT.SRC 2014}
@@
             {\iai~/~\iise~/~\icsn, \fiit}
+% Within the `affiliation' parameter you can use the `\fiit' macro to
+% generate the full name of our faculty.
 \mail{novak@fiit.stuba.sk}
@@
 
+\section*{Extended Abstract}
+
+This is a simple example of an ``extended abstract''. These documents should not exceed two pages. Please, do not use the
+\begin{verbatim}
     \begin{abstract}
-All IIT.SRC \LaTeX{} contributions are expected to use the {\tt iitsrc}
-class. This document was typeset with that class and as such it is
-solely a demo. It is a supplement to the {\tt iitsrc.pdf} document which
-describes all the (boring) things in detail.\footnotemark
+    ...
     \end{abstract}
+\end{verbatim}
+environment. Instead, put your whole text in a single unnumbered section introduced with the following command:
+\begin{verbatim}
+    \section*{Extended Abstract}
+\end{verbatim}
+Inside this single section you can use usual \LaTeX{} commands.
 
-\section{Basics}
-%
-\footnotetext{Abstract should be no longer than 100 words.}
-%
-We do not hope to give you as extensive information as other sources (such
-as~\cite{lamport:latex}). On Linux you can get fairly complete
-information about \LaTeX{} commands via:
-
-\begin{verbatim}
-    info latex
-\end{verbatim}
-Here we only make few notes concerning obvious things you probably
-already know.
-%
-You should properly divide your text into several sections (via
-\verb|\section| and perhaps also \verb|\subsection| commands.)
-%
-Do not change the font family and font sizes defined by the
-\verb|iitsrc| class. These default values should be common for all
-articles.
-%
-If you want to emphasize something (perhaps a newly introduced notion
-or such), use the \verb|\em| command.
-%
-Usage of the bold face (the \verb|\bf| command) is very unusual in
-normal \LaTeX{} text. It is not advised to use it explicitly.
-%
-End of a paragraph is indicated in the source code by an empty line.
-%
-You can use usual environments such as \verb|itemize| or
-\verb|enumerate| to create bulleted or enumerated lists.
-%
-\section{Mathematical formul\ae, equations, figures and tables}
-%
-The \verb|equation| environment can be used for typesetting numbered
-equations.
-\begin{equation}
-\label{eq:contestwinner}
-e^{i\pi}+1=0
-\end{equation}
-It was produced with a following commands:
-\begin{verbatim}
-   \begin{equation}
-   e^{i\pi}+1=0
-   \end{equation}
-\end{verbatim}
-If you want later to refer to your equation, it is wise to accompany
-your equation with a symbolic label, for example as below:
-\begin{verbatim}
-   \begin{equation}
-   \label{eq:contestwinner}
-   e^{i\pi}+1=0
-   \end{equation}
-\end{verbatim}
-Now you can refer to it---the
-Equation~\ref{eq:contestwinner}---by its
-symbolical name rather than a concrete number. This is advantageous
-because the order of equations might change over time. This reference
-can be typeset as follows:
-\begin{verbatim}
-   Equation~\ref{eq:contestwinner}
-\end{verbatim}
-There is also \verb|equation*| environment which enables you to
-typeset unnumbered equation.
-
-There are also other useful \LaTeX{} commands and environments such as
-\verb|eqnarray|. For example:
-\begin{eqnarray}
-x & \ll  & y_1 + \cdots + y_n\\
-x & \leq & z
-\end{eqnarray}
-It enables you to put (non-)equalities nicely one below the other
-pleasantly aligned. The above example was typeset by a following
-command:
-\begin{verbatim}
-   \begin{eqnarray}
-   x & \ll  & y_1 + \cdots + y_n\\
-   x & \leq & z
-   \end{eqnarray}
-\end{verbatim}
-%
-If you need to typeset a table such as Table~\ref{tab:strategy}
-\begin{table}[ht]
-    \caption{Specification of a strategy  $s(a)$ of agent $a$.}
-    \label{tab:strategy}
-    \begin{center}
-        \begin{tabular}{|c|c|c|c|}
-        \hline
-        & penalty & penalty & movement\\
-        & of agent $a$ & of agent $b$ & of agent $a$\\
-        \hline
-        1 & $p(a)=0$ & $p(b)=0$ & $S_1(a)$\\
-        2 & $p(a)=0$ & $p(b)>0$ & $S_2(a)$\\
-        3 & $p(a)>0$ & $p(b)=0$ & $S_3(a)$\\
-        4 & $p(a)>0$ & $p(b)>0$ & $S_4(a)$\\
-        \hline
-    \end{tabular}
-\end{center}
-\end{table}
-you can do it as follows:
-\begin{verbatim}
-    \begin{table}[ht]
-        \caption{Specification of a strategy
-                 $s(a)$ of agent $a$.}
-        \label{tab:strategy}
-        \begin{center}
-            \begin{tabular}{|c|c|c|c|}
-            \hline
-            & penalty & penalty & movement\\
-            & of agent a & of agent b & of agent a\\
-            \hline
-            1 & $p(a)=0$ & $p(b)=0$ & $S_1(a)$\\
-            2 & $p(a)=0$ & $p(b)>0$ & $S_2(a)$\\
-            3 & $p(a)>0$ & $p(b)=0$ & $S_3(a)$\\
-            4 & $p(a)>0$ & $p(b)>0$ & $S_4(a)$\\
-            \hline
-        \end{tabular}
-    \end{table}
-\end{verbatim}
-%
-If you need to include a figure to your document,
-such as Figure~\ref{fig:fractaltree},
-\begin{figure}[t]
-    \begin{center}
-        \includegraphics{tree}
-        \caption{Fractal tree.}
-        \label{fig:fractaltree}
-    \end{center}
-\end{figure}
-you can do it as follows:
-\begin{verbatim}
-    \begin{figure}[h]
-        \begin{center}
-            \includegraphics{tree}
-            \caption{Fractal tree}
-            \label{fig:fractaltree}
-       \end{center}
-   \end{figure}
-\end{verbatim}
-If you process your document with \LaTeX\ you will have to
-provide all your figures as EPS (Encapsulated Postscript) files.
-If you process your document with PDF\LaTeX\ you will have to
-provide all your figures as PDF files. Several graphical programs
-are able to export pictures to these two formats.
-If possible, please use a
-vector editor. Please do not convert bitmaps into EPS or PDF.
-The printed results are then usually ugly.
-
-Note that since you have given a figure a symbolic name (in this case
-\verb|fig:fractaltree|), you can refer to this figure as follows:
-\begin{verbatim}
-   Figure~\ref{fig:fractaltree}
-\end{verbatim}
-This is advantageous because regardless of the fact how you reorder
-your figures in the document, the references to them will never
-break unless you change their symbolical name.
-%
-Do not forget to describe your figure with a \verb|\caption| command.
-%
-Due to technological constraints, included figures should be
-\begin{itemize}
-\item black-and-white,
-\item minimal thickness of lines should be at least 0.25 mm,
-\item do not use half-tones; use raster instead to express various
-degrees of gray.
-\end{itemize}
-%
-If you need to insert a pseudo code of an algorithm into the
-paper, you can use the algorithms package for \LaTeX.
-Documentation and example in \TeX{} file can be found in the zip
-file available on
-\verb|http://texcatalogue.sarovar.org/entries/algorithms.html|
-%
-Please do not refer to various parts
-of your document via page numbers. Instead, give a symbolic name
-to your sections (via \verb|\label| command) and refer to your
-sections via \verb|\ref| command.
-%
-Please leave the \verb|\editpages| command from a ``minimal article
-source code'' in place. Its
-purpose is related to combining particular articles to a single volume
-and if you delete it, someone will have later add it back. So if you
-leave it where it is, you will save yours someone else's time.
-%
-\section{The bibliography}
-%
-
-\def\BibTeX{{\rmfamily B\kern-.05em%
-    \textsc{i\kern-.025em b}\kern-.08em%
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-\LaTeX{} document usually creates bibliography references via \BibTeX.
-Basic information about \BibTeX{} is in~\cite{lamport:latex}. You are
-encouraged to use it too. Bibliography references are usually inserted
-in the document as follows:
-\begin{verbatim}
-   \bibliography{common}
-   \bibliographystyle{iitsrc}
-\end{verbatim}
-Be sure to use the \verb|iitsrc| style as suggested above. We used \BibTeX{}
-also for typesetting bibliographic references cited within this
-document. So you can look at the source code ({\tt demo.tex}) and the
-compilation instructions ({\tt Makefile}) to see how it was
-generated. The {\tt common.bib} file contains the bibligraphy resources
-we collected over time. There are various entries in the form:
-\begin{verbatim}
-    @ARTICLE{OwickiGries76b,
-        AUTHOR = {S. Owicki and D. Gries},
-        TITLE = "Verifying Properties of Parallel Programs,
-                 an axiomatic approach",
-        JOURNAL = cacm,
-        VOLUME = 19,
-        NUMBER = 5,
-        PAGES = {279-285},
-        MONTH = may,
-        YEAR = 1976
-    }
-\end{verbatim}
-Each such entry contains logical information about the particular source
-of information. You can add your sources of information therein. Some
-information about how to do that can be found in~\cite{lamport:latex}
-(Appendix B).  \BibTeX{} finds out which ones you cite within your
-document and format the data it finds in your {\tt *.bib} (in this case
-{\tt common.bib}) file according to the instructions in the {\tt *.bst}
-(in this case {\tt iitsrc.bst}) file. All you have to do within your
-document is to \verb|\cite{key}| them.
-
-Other example citated
-sources:~\cite{CHS03RR,friedman:switching,henessy:computer,henrio:thesis,MannaPnueli82,MisraChandy,OwickiGries76b,vardhan98distributed,WidomPanangaden,C99-draft,czarnecki:generative-programming,SWIG,leiserson:network}
-
-\begin{itemize}
-\item Item
-    \begin{itemize}
-    \item Item
-        \begin{itemize}
-        \item Item
-
-        \end{itemize}
-    \end{itemize}
-\end{itemize}
-
-\begin{enumerate}
-\item Item
-    \begin{enumerate}
-    \item Item
-        \begin{enumerate}
-        \item Item
-
-        \end{enumerate}
-    \end{enumerate}
-\end{enumerate}
+\nocite{lamport:latex}
 

### 2014-02-18 paper/paper.tex
feat(paper): create paper

\documentclass{iitsrc}
\usepackage{graphicx}
\usepackage{mflogo}
\usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
%\PrerenderUnicode{áäčďéíľĺňóôŕšťúýžÁÄČĎÉÍĽĹŇÓÔŔŠŤÚÝŽ}

% Please do not remove the following commands:
\editpages{1}{8}

\title{Beyond Adaptive Web Design}
\titlerunning{Beyond Adaptive Web Design}
\author{Ján}{Antala}
\author{Michal}{Čerňanský}
\supervision{\ms}
            {\infosys}
            {~Assoc.~Professor}
            {\iai, \fiit}
\mail{hello@janantala.com}
\field{Web Science and Web Engineering}

\begin{document}

\begin{abstract}
Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also new kinds of internet connection. But there are not just smartphones and desktop computers. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles and more. So it is necessary to adapt web pages for different devices and new interaction methods. In our work, we follow Mobile First and Progressive Enhancement design, which emphasises a great performance on mobile devices and later profit on high-end computers. We present a new way of web components adaptation based on a device features and external conditions in our work and new possibilities of interaction with web application based on speech recognition, motion or device rotation. The evaluation of the proposed method of adaptation shows slightly better results than original approach.
\end{abstract}

\section{Introduction}

The Web is continually evolving and we need to evolve with it. It used to be easier to manage browsers when there were just a few of them on the desktop. Today we not only have to deal with a wide range of desktop browsers but mobile devices, tablets, televisions, weareable devices and more. Even for the average web site things have changed a lot over four years: browser share, operating systems, screen resolutions, and more~\cite{ui17}.

The basic approach how to provide an optimal viewing experience is to use Responsive web design which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}. While creating flexible layouts is important, there’s a whole lot more that goes into truly exceptional adaptive web experiences. The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.

The power of the web is its ubiquity. No one knows what the landscape is going to look like in a couple years, but there’s a good chance the new devices in a few years from now will have access to the web. Because of this, we need to preserve and embrace the web’s ubiquity. This requires us to deliver full web experiences regardless of how and where people access the web. It's important to continue creating flexible interfaces that can adapt to any screen size. Performance often takes a back seat to everything else. Progressive enhancement, feature detection and many other techniques allow us to build up a core experience that allow us to support more devices while still optimizing for the the best of the best. The key aspect of Future Friendly thinking is to acknowledge and embrace unpredictability. Nobody knows where things are going but the one thing we can count on is the evolution.

Adaptive web design is essentially progressive enhancement at its core, but it’s being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles and more. We also have many types of internet connections with different qualities.

Responsive design is one technique in an adaptive web design strategy. Creating flexible layouts is extremely important, but it’s just one piece of the puzzle. It’s also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.

We consider “adaptive web design” as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.

\section{Adaptive Input methods}

As we have many types of devices with web access we also have to adapt input methods for them. It is not just about screen sizes, but many displays also have touch capabilities.

Web browsers on TVs are actually really good but the input is terrible so no one uses them. Input is much more important to interface design than screen size. The input defines what a design needs to do in order to accomplish a task~\cite{adaptiveinput}.

We also have wearable computers. The current Google Glass interface is limited to a floating rectangle above head. We don’t have full range of motion and, as a result, no spatial cues or depth in the interface.

There is no one true input for the Web. We have to contend with fingers, mice, keyboards, voice and more. The challenge for us over the next few years is not designing for one input but many.

\subsection{Touch} % (fold)
\label{sub:touch}

Touch is no longer just isolated to smartphones and tablets. Many big sreens in laptops or desktops nowadays are touch capable. Every desktop design has to be touch-friendly now.

The optimal touch target size is 7mm, based on the average size of human finger tips and pads. CSS2.1 defines a pixel as 1/96 of an inch. So 7mm should be 30pixels~\cite{designingfortouch}. However, things aren’t so easy because of dynamic viewports. It means that input elemtents in website have to be usually bigger.

The best touch interface is sometimes no touch at all. We can use sensors and speech input which is the next frontier for interaction design.

% subsection touch (end)

\subsection{Speech} % (fold)
\label{sub:speech}

The speech input aims to provide an alternative input method for web applications, without using a keyboard or other physical device. This is no longer science fiction but reality. Many companies rely on it and deploy it to the modern devices and software. It could be also benefitial for older or disabled users~\cite{SpeechRecognition} and can easily become the next big thing.

We can now use speech recognition to take a full control of the web site as we have access to continuous recognition stream. We don't need another input methods at all. A speech feedback for user interaction is also important and we can use speech synthesis feature for it.

% subsection speech (end)

\subsection{Device motion} % (fold)
\label{sub:device_motion}

We can use a lot of sensors in the devices to detect the device motion. It is made possible by a combination of always-on sensors as are an accelerometer a gyroscope, and a magnetometer, that tell us a lot about how a device is moving through the space around it. The ability of these sensors to provide precise information about the movement of a device opens up new design possibilities for web applications~\cite{ultrabooks}.

From controlling the user interface based on three dimensional motion as input, to combining device motion with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}. There's a lot of interesting interface designs made possible by Device Motion. It depends on us how we use them.

% subsection device_motion (end)

\subsection{Video Motion} % (fold)
\label{sub:video_motion}

Many modern devices contains built in video camera sensor which we can use as alternative method to device motion. We can access video stream and analyse landscape around the device. Video motion detection is a way of defining user activity in a scene by analyzing image data and differences in a series of images.

We can detect user motion and use it as an alternatove part of input method. We can build web games and another real time interfaces. There's again a lot of interesting interface designs made possible.

% subsection video_motion (end)

\section{Adaptive Web Components} % (fold)
\label{sec:adaptive_web_components}

One of the most common critiques against responsive Web design is that Web sites have large file size and so they are slowing Web pages down. But we can make responsive sites perform well, we just have to the work to make it possible~\cite{20mb}.

We all should care about page speed and mobile performance because people need fast experiences on the Web. There's lot of studies that highlight the importance of speed. More than half of people with a bad loading experience on mobile, won't come back~\cite{performancebrowsernetworking}. 73\% of mobile internet users say they've encountered Web pages that are too slow. A 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}. Speed is an esencial part of our strategy and we should care about it. We can quantify its impact on the metrics and track it.

There are many different types of internet connections. Mobile network speeds have gone up but this doesn't help much as page load times tend to plateau as bandwidth increases. Latency is a much bigger contribution to download times. LTE reduces tower latency by several milliseconds but we still need to make a number of connections to get data to our phone~\cite{performancebrowsernetworking}.

So what we should do about it? We can create reuseable components and conditionaly load resources. Web components allow us to use custom HTML elements in the browser. We can wrap up a simple element or an entire application logic within an HTML element~\cite{webcomponents}. We can create Web applications in a reusable, modular and encapuslated way.

% section adaptive_web_components (end)

\section{Evaluation and experiments} % (fold)
\label{sec:evaluation_and_experiments}

There have been made series of experiments on both adaptive input methods and web components. The goal has been to create reusable modules and components every developer can include into their web application. All of them have been released as open source and are available on GitHub.

We have tracked amount of saved web traffic, interest in alternative input methods and received a lot of feedback from the community.

\subsection{Input methods} % (fold)
\label{sub:input_methods}

Adaptive input methods provide alternative way of web application control and extend current approach. We have been experimenting to control web applications using voice commands, gyroscope motion and video motion.

\subsubsection{Voice commands} % (fold)
\label{ssub:voice_commands}

Speech input provides a great opportunity to take a complete control over web application using only voice commands. For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reuseable module. Speech recognition is however currently possible online only.

Using speech recognition we get an utterance string which can be compared to voice commands from our configuration. We use regular expressions for this purpose with attached callback methods. These configurations are bound to utterance watchers and the callback is called when voice command is recognised. Regular expressions are benefitial since we can set up a single watcher for dynamical commands where one command can be used for multiple subjects.

But there are many more interesting things we can achieve using speech input. We can even use multiple languages for speech recognition. One of the biggest problems of the voice commands is however incorrect speech recognition. To solve this issue we can conditionalize regular expressions or use uterance error correction.

% subsubsection voice_commands (end)

\subsubsection{Gyroscope rotation} % (fold)
\label{ssub:gyroscope_rotation}

We have used device orientation API as alternative control method to web application and built a module which can scroll in website using gyroscope rotation. Developers can use this module as replacement of the global application scroll instead of touch events or mice wheel and also a local element scroll too.

We have access to 3 axis rotation informations which are recalculated every time on device orientation change. We remember starting device orientation and compare it to the current one. Based on this substraction we can make a decision which direction we scroll and how fast. The bigger the orientation difference is, the faster we scroll.

\begin{figure}[h]
    \begin{center}
        \includegraphics[width=0.25\textwidth]{../images/gyroscope}
        \caption{Scrolling in the webpage by gyroscope}
        \label{fig:gyroscope}
    \end{center}
\end{figure}

However some problems have been detected. The biggest one is that browser vendors don't use specification correctly and use own orientation ranges and directions. This causes some scroll issues.

% subsubsection gyroscope_rotation (end)

\subsubsection{Video camera motion} % (fold)
\label{ssub:video_camera_motion}

Almost every moder device contains a video camera. This is a great opportunity to introduce video motion to web applications. We can control web sites using motion gestures.

We use a video camera stream and devide it into image frames. Then we can detect a website user in the each frame using a hsv filter. When we compare all pixels in two adjacent frames we get difference points. When we apply this comparision to multiple frames we can calculate a motion vector.

\begin{figure}[h]
    \begin{center}
        \includegraphics[width=0.75\textwidth]{../images/videomotion}
        \caption{Converting video stream into motion vector}
        \label{fig:videomotion}
    \end{center}
\end{figure}

We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom. Using video camera motion we can enhance experience in websites and games. However we need a proper ambient lighting. There can be detection issues in too dark and too light scenes.

% subsubsection video_camera_motion (end)

% subsection input_methods (end)

\subsection{Web Components} % (fold)
\label{sub:web_components}

There are a lot of commonly used web services that produce unnecessary traffic. Elements like videos or maps are a common part of the most web sites. All of them produces many requests and the web traffic even the website user doesn't want to watch the video or browse the map. There are also native mobile application for that services with better perfomance. So what can we to do? This is actually a great opportunity to utilize conditional loading to serve the best experience for the right context.

We use the Mobile First principe so we make a default elemet static and pull in a static image. This approach saves a lot of web traffic and becasue of limited mobile internet plans also user's money. We can then detect when it’s appropriate to download the embedded map or to launch the native mobile application.

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.62\textwidth]{../images/maps.png}
        \caption{Maps component}
        \label{fig:maps}
    \end{center}
\end{figure}

By default we set an anchor to the location of the service website. When a user taps the component, the browser will try to open the native application where they can have a better experience. If the native experience is unavailable, the user is redirected to the service website, where they receive a full-screen experience. However, we don't always want to open the native application. We can download an embedded map or play the video directly after the tap. The user can interact with them directly in the web application so developers have to make a decision between these choices.

This approach works quite well for simple use cases. We can show multiple map types, markers or videos. However, more interactive elements require additional consideration. Even then use of an embedded elements directly still might not make sense because of unnecessary traffic, while adaptive techniques reduces it. We can still replace basic static image with richer elements. Adaptive web componets are a decent baseline.

% subsection web_components (end)

% section evaluation_and_experiments (end)

\section{Conclusion} % (fold)
\label{sec:conclusion}

We have received a lot feedback and have usage and popularity results of adaptive input methods. As we have expected the most popular input method is speech input as we can control an entire web application using only voice commands. Gyroscope and video motion are also useful input methods, but there are limited occasions where to use them and can be used as supplementary input method only. All of them however provide a great opportunity to enhance user experience.

Adaptive web components are a great to save an unwonted web traffic. They also icrease user experience because the web page produces less requests and loads faster. However the limitations also exist because many websites need custom elements and design. As a result the adaptive web components produce less interest than adaptive input methods.

More changes are coming, new devices, web APIs and beyond. What will it look like in a couple of years? The devices will be more diversified and have the web access. So we have to prepare the Web to this evolution and provide the best user experience.

% section conclusion (end)

\bibliography{common}
\bibliographystyle{iitsrc}
\end{document}

### 2014-02-19 paper/paper.tex
fix(paper): fix author
refactor(): extend Adaptive Input methods
refactor(): extend Evaluation and experiments

@@
 \author{Ján}{Antala}
-\author{Michal}{Čerňanský}
 \supervision{\ms}
             {\infosys}
-            {~Assoc.~Professor}
+            {~Assoc.~Professor Michal Čerňanský}
             {\iai, \fiit}
@@
 
-As we have many types of devices with web access we also have to adapt input methods for them. It is not just about screen sizes, but many displays also have touch capabilities.
+As we have many types of devices with web access we also have to adapt input methods for them.
+It is not just about screen sizes, but many displays also have touch capabilities, are equiped with microphone, accelerometer, gyroscope or camera.
 
@@
 There have been made series of experiments on both adaptive input methods and web components.
-The goal has been to create reusable modules and components every developer can include into their web application.
+To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects.
 All of them have been released as open source and are available on GitHub.

### 2014-02-19 paper/paper.tex
refactor(): rewrite Abstract

@@
 \begin{abstract}
-Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also new kinds of internet connection.
+Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also high-latency networks.
 But there are not just smartphones and desktop computers.
-We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles and more.
+We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
 So it is necessary to adapt web pages for different devices and new interaction methods.
-In our work, we follow Mobile First and Progressive Enhancement design, which emphasises a great performance on mobile devices and later profit on high-end computers.
+Several new methods for designing web are rapidly evolving.
 We present a new way of web components adaptation based on a device features and external conditions in our work and new possibilities of interaction with web application based on speech recognition, motion or device rotation.
-The evaluation of the proposed method of adaptation shows slightly better results than original approach.
 \end{abstract}
@@
 Adaptive web design is essentially progressive enhancement at its core, but it’s being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined.
-We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles and more.
+We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
 We also have many types of internet connections with different qualities.

### 2014-02-19 paper/paper.tex
style: fix quotation

@@
 The basic approach how to provide an optimal viewing experience is to use Responsive web design which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
-While creating flexible layouts is important, there’s a whole lot more that goes into truly exceptional adaptive web experiences.
+While creating flexible layouts is important, there's a lot more that goes into truly exceptional adaptive web experiences.
 The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.
@@
 The power of the web is its ubiquity.
-No one knows what the landscape is going to look like in a couple years, but there’s a good chance the new devices in a few years from now will have access to the web.
-Because of this, we need to preserve and embrace the web’s ubiquity.
+No one knows what the landscape is going to look like in a couple years, but there's a good chance the new devices in a few years from now will have access to the web.
+Because of this, we need to preserve and embrace the web's ubiquity.
 This requires us to deliver full web experiences regardless of how and where people access the web.
@@
 
-Adaptive web design is essentially progressive enhancement at its core, but it’s being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined.
+Adaptive web design is essentially progressive enhancement at its core, but it's being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined.
 We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
@@
 Responsive design is one technique in an adaptive web design strategy.
-Creating flexible layouts is extremely important, but it’s just one piece of the puzzle.
-It’s also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.
+Creating flexible layouts is extremely important, but it's just one piece of the puzzle.
+It's also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.
 
-We consider “adaptive web design” as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.
+We consider ``adaptive web design'' as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.
 
@@
 The current Google Glass interface is limited to a floating rectangle above head.
-We don’t have full range of motion and, as a result, no spatial cues or depth in the interface.
+We don't have full range of motion and, as a result, no spatial cues or depth in the interface.
 
@@
 So 7mm should be 30pixels~\cite{designingfortouch}.
-However, things aren’t so easy because of dynamic viewports.
+However, things aren't so easy because of dynamic viewports.
 It means that input elemtents in website have to be usually bigger.
@@
 This approach saves a lot of web traffic and becasue of limited mobile internet plans also user's money.
-We can then detect when it’s appropriate to download the embedded map or to launch the native mobile application.
+We can then detect when it's appropriate to download the embedded map or to launch the native mobile application.
 

### 2014-02-19 paper/paper.tex
refactor(): rewrite Introduction

@@
 
-The basic approach how to provide an optimal viewing experience is to use Responsive web design which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
-While creating flexible layouts is important, there's a lot more that goes into truly exceptional adaptive web experiences.
+The basic approach how to provide an optimal viewing experience is to use ``Responsive web design'' which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
+While creating flexible layouts is important, there's a lot more that requires exceptional adaptive web experiences.
 The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.
@@
 The power of the web is its ubiquity.
-No one knows what the landscape is going to look like in a couple years, but there's a good chance the new devices in a few years from now will have access to the web.
+No one knows what the landscape is going to appear in a couple years, but there's a reasoneable probability the new devices in a few years from now will have access to the web.
 Because of this, we need to preserve and embrace the web's ubiquity.
-This requires us to deliver full web experiences regardless of how and where people access the web.
-It's important to continue creating flexible interfaces that can adapt to any screen size.
-Performance often takes a back seat to everything else.
-Progressive enhancement, feature detection and many other techniques allow us to build up a core experience that allow us to support more devices while still optimizing for the the best of the best.
-The key aspect of Future Friendly thinking is to acknowledge and embrace unpredictability.
-Nobody knows where things are going but the one thing we can count on is the evolution.
+This requires us to provide full web experiences regardless of how and where people access the web.
+It's important to remain in creating flexible interfaces that can adapt to any screen size.
+Performance is often less important to everything else.
+``Progressive enhancement'', feature detection and many other techniques allow us to increase experience that allow us to support more devices while still optimizing for the finest.
+The key aspect of ``Future Friendly'' thinking is to acknowledge and embrace unpredictability.
+Nobody knows where things are going but the one thing we can trust is the evolution.
 
-Adaptive web design is essentially progressive enhancement at its core, but it's being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined.
+Adaptive web design is fundamentally progressive enhancement, but it's being applied to a much larger and more diverse landscape.
 We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
-We also have many types of internet connections with different qualities.
+We also have many types of internet networks with different speed, latency and quality.
+Responsive design is also one technique in an adaptive web design strategy.
+Creating flexible layouts is important, but there are many more factors we need to think about.
+It's also important to consider as well ergonomics, touch capability, other input methods, internet connections and many other features that can be detected.
 
-Responsive design is one technique in an adaptive web design strategy.
-Creating flexible layouts is extremely important, but it's just one piece of the puzzle.
-It's also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.
-
-We consider ``adaptive web design'' as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.
+We consider ``adaptive web design'' as a equal to creating a single Web experience that modifies based on the capabilities of the device and browser.
+Website can access sensors in devices and use them to enhance user experience.
 

### 2014-02-20 paper/paper.tex
refactor(paper): refactor build
refactor: restyle sentences

@@
 \editpages{1}{8}
+\hyphenation{pha-blets}
 
@@
 
-We consider ``adaptive web design'' as a equal to creating a single Web experience that modifies based on the capabilities of the device and browser.
+We consider ``adaptive web design'' as an equal with creating a single Web experience that adjusts based on the capabilities of the device and browser.
 Website can access sensors in devices and use them to enhance user experience.
@@
 
-\subsection{Touch} % (fold)
+\paragraph{Touch} % (fold)
 \label{sub:touch}
@@
 
-% subsection touch (end)
+% paragraph touch (end)
 
-\subsection{Speech} % (fold)
+\paragraph{Speech} % (fold)
 \label{sub:speech}
@@
 
-% subsection speech (end)
+% paragraph speech (end)
 
-\subsection{Device motion} % (fold)
+\paragraph{Device motion} % (fold)
 \label{sub:device_motion}
@@
 
-% subsection device_motion (end)
+% paragraph device_motion (end)
 
-\subsection{Video Motion} % (fold)
+\paragraph{Video Motion} % (fold)
 \label{sub:video_motion}
@@
 
-% subsection video_motion (end)
+% paragraph video_motion (end)
 
@@
 
-\subsubsection{Voice commands} % (fold)
+\paragraph{Voice commands} % (fold)
 \label{ssub:voice_commands}
@@
 
-% subsubsection voice_commands (end)
+% paragraph voice_commands (end)
 
-\subsubsection{Gyroscope rotation} % (fold)
+\paragraph{Gyroscope rotation} % (fold)
 \label{ssub:gyroscope_rotation}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \begin{center}
-        \includegraphics[width=0.25\textwidth]{../images/gyroscope}
+        \includegraphics[width=0.2\textwidth]{../images/gyroscope}
         \caption{Scrolling in the webpage by gyroscope}
@@
 
-% subsubsection gyroscope_rotation (end)
+% paragraph gyroscope_rotation (end)
 
-\subsubsection{Video camera motion} % (fold)
+\paragraph{Video camera motion} % (fold)
 \label{ssub:video_camera_motion}
 
-Almost every moder device contains a video camera. This is a great opportunity to introduce video motion to web applications. We can control web sites using motion gestures.
-
+Almost every moder device contains a video camera.
+This is a great opportunity to introduce video motion to web applications.
+We can control web sites using motion gestures.
 We use a video camera stream and devide it into image frames.
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \begin{center}
-        \includegraphics[width=0.75\textwidth]{../images/videomotion}
+        \includegraphics[width=0.7\textwidth]{../images/videomotion}
         \caption{Converting video stream into motion vector}
@@
 
-% subsubsection video_camera_motion (end)
+% paragraph video_camera_motion (end)
 
@@
 So what can we to do?
-This is actually a great opportunity to utilize conditional loading to serve the best experience for the right context.
+This is a great opportunity to utilize conditional loading to serve the best experience for the right context.
 
@@
     \begin{center}
-        \includegraphics[width=0.62\textwidth]{../images/maps.png}
+        \includegraphics[width=0.7\textwidth]{../images/maps.png}
         \caption{Maps component}

### 2014-02-20 paper/paper.tex
refactor: verify the usefulness of the proposed concept

@@
 \usepackage{mflogo}
+\usepackage{url}
 \usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
@@
 % Please do not remove the following commands:
-\editpages{1}{8}
+\editpages{1}{6}
 \hyphenation{pha-blets}
@@
 
+We have detected several web componenets and input methods and tried to verify which of them is more useful for the web developers.
 There have been made series of experiments on both adaptive input methods and web components.
 To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects.
-All of them have been released as open source and are available on GitHub.
+All of them have been released as open source and are available on GitHub~\footnotemark.
 
-We have tracked amount of saved web traffic, interest in alternative input methods and received a lot of feedback from the community.
+\footnotetext{The modules and components we used to verify the usefulness of the proposed concept are available on GitHub \url{https://github.com/angular-adaptive}}
+
+We have tracked amount of saved web traffic and web requests, webpage rendering time and interest in alternative input methods.
+We have also received a lot of feedback from the community which helped us to verify the proposed concept.
 
@@
     \begin{center}
-        \includegraphics[width=0.7\textwidth]{../images/videomotion}
+        \includegraphics[width=0.8\textwidth]{../images/videomotion}
         \caption{Converting video stream into motion vector}
@@
     \begin{center}
-        \includegraphics[width=0.7\textwidth]{../images/maps.png}
+        \includegraphics[width=0.8\textwidth]{../images/maps.png}
         \caption{Maps component}

### 2014-02-20 paper/paper.tex
refactor(paper): refactor paper parts

@@
 The basic approach how to provide an optimal viewing experience is to use ``Responsive web design'' which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
-While creating flexible layouts is important, there's a lot more that requires exceptional adaptive web experiences.
+While creating flexible layouts is important, there's a lot more that requires remarkable adaptive web experiences.
 The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.
@@
 The input defines what a design needs to do in order to accomplish a task~\cite{adaptiveinput}.
-
 We also have wearable computers.
-The current Google Glass interface is limited to a floating rectangle above head.
+The current Google Glass interface is limited to a floating display above head.
 We don't have full range of motion and, as a result, no spatial cues or depth in the interface.
@@
 
-\paragraph{Touch} % (fold)
+\subsubsection*{Touch} % (fold)
 \label{sub:touch}
@@
 
-% paragraph touch (end)
+% subsubsection touch (end)
 
-\paragraph{Speech} % (fold)
+\subsubsection*{Speech} % (fold)
 \label{sub:speech}
@@
 
-% paragraph speech (end)
+% subsubsection speech (end)
 
-\paragraph{Device motion} % (fold)
+\subsubsection*{Device motion} % (fold)
 \label{sub:device_motion}
@@
 
-% paragraph device_motion (end)
+% subsubsection device_motion (end)
 
-\paragraph{Video Motion} % (fold)
+\subsubsection*{Video Motion} % (fold)
 \label{sub:video_motion}
@@
 
-% paragraph video_motion (end)
+% subsubsection video_motion (end)
 
@@
 
-We all should care about page speed and mobile performance because people need fast experiences on the Web.
+We all should be interested in page speed and mobile performance because people need fast experiences on the Web.
 There's lot of studies that highlight the importance of speed.
 More than half of people with a bad loading experience on mobile, won't come back~\cite{performancebrowsernetworking}.
-73\% of mobile internet users say they've encountered Web pages that are too slow.
-A 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
+73\% of mobile internet users say they've encountered Web pages that are too slow, a 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
 Speed is an esencial part of our strategy and we should care about it.
@@
 There are many different types of internet connections.
-Mobile network speeds have gone up but this doesn't help much as page load times tend to plateau as bandwidth increases.
-Latency is a much bigger contribution to download times.
-LTE reduces tower latency by several milliseconds but we still need to make a number of connections to get data to our phone~\cite{performancebrowsernetworking}.
+Mobile network speeds have rose but this doesn't help much as page load times are still high as bandwidth increases.
+Latency is a much bigger fragment to download times.
+LTE reduces tower latency by several milliseconds but we still need to make a number of connections to download data to our devices~\cite{performancebrowsernetworking}.
 
@@
 Web components allow us to use custom HTML elements in the browser.
-We can wrap up a simple element or an entire application logic within an HTML element~\cite{webcomponents}.
-We can create Web applications in a reusable, modular and encapuslated way.
+We can enclose a simple element or an entire application logic within an HTML element~\cite{webcomponents}.
+We can build Web applications in a reusable, commutable and encapuslated way.
 
@@
 
-We have detected several web componenets and input methods and tried to verify which of them is more useful for the web developers.
-There have been made series of experiments on both adaptive input methods and web components.
+We have detected several web componenets and input methods and tried to verify which of them provide better experience for the website users and are also useful for the web developers.
+There have been made series of experiments on both adaptive input methods and adaptive web components.
 To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects.
@@
 
-\paragraph{Voice commands} % (fold)
+\subsubsection*{Voice commands} % (fold)
 \label{ssub:voice_commands}
@@
 
-% paragraph voice_commands (end)
+% subsubsection voice_commands (end)
 
-\paragraph{Gyroscope rotation} % (fold)
+\subsubsection*{Gyroscope rotation} % (fold)
 \label{ssub:gyroscope_rotation}
@@
     \begin{center}
-        \includegraphics[width=0.2\textwidth]{../images/gyroscope}
+        \includegraphics[width=0.15\textwidth]{../images/gyroscope}
         \caption{Scrolling in the webpage by gyroscope}
@@
 
-% paragraph gyroscope_rotation (end)
+% subsubsection gyroscope_rotation (end)
 
-\paragraph{Video camera motion} % (fold)
+\subsubsection{Video camera motion} % (fold)
 \label{ssub:video_camera_motion}
@@
     \begin{center}
-        \includegraphics[width=0.8\textwidth]{../images/videomotion}
+        \includegraphics[width=0.5\textwidth]{../images/videomotion}
         \caption{Converting video stream into motion vector}
@@
 
-% paragraph video_camera_motion (end)
+% subsubsection video_camera_motion (end)
 
@@
 All of them produces many requests and the web traffic even the website user doesn't want to watch the video or browse the map.
-There are also native mobile application for that services with better perfomance.
+There are also native mobile application for that services with better perfomance which provide full user experience.
 So what can we to do?
@@
     \begin{center}
-        \includegraphics[width=0.8\textwidth]{../images/maps.png}
+        \includegraphics[width=0.55\textwidth]{../images/maps.png}
         \caption{Maps component}
@@
 We can still replace basic static image with richer elements.
-Adaptive web componets are a decent baseline.
 
@@
 We have received a lot feedback and have usage and popularity results of adaptive input methods.
-As we have expected the most popular input method is speech input as we can control an entire web application using only voice commands.
+As we have expected, the most popular input method is speech input since we can control an entire web application using only voice commands.
 Gyroscope and video motion are also useful input methods, but there are limited occasions where to use them and can be used as supplementary input method only.
@@
 However the limitations also exist because many websites need custom elements and design.
-As a result the adaptive web components produce less interest than adaptive input methods.
+As a result the adaptive web components produce less interest than adaptive input methods, but are the necessary part of the Web.
 
@@
 The devices will be more diversified and have the web access.
-So we have to prepare the Web to this evolution and provide the best user experience.
+So we have to prepare the Web to this evolution and provide the best user experience, design for many inputs and save the inessential web traffic.
 

### 2014-03-15 paper/paper.tex
fix: fix typos

@@
 The power of the web is its ubiquity.
-No one knows what the landscape is going to appear in a couple years, but there's a reasoneable probability the new devices in a few years from now will have access to the web.
+No one knows what the landscape is going to appear in a couple years, but there's a reasonable probability the new devices in a few years from now will have access to the web.
 Because of this, we need to preserve and embrace the web's ubiquity.
@@
 
-Touch is no longer just isolated to smartphones and tablets. Many big sreens in laptops or desktops nowadays are touch capable. Every desktop design has to be touch-friendly now.
+Touch is no longer just isolated to smartphones and tablets. Many big screens in laptops or desktops nowadays are touch capable. Every desktop design has to be touch-friendly now.
 
@@
 Many companies rely on it and deploy it to the modern devices and software.
-It could be also benefitial for older or disabled users~\cite{SpeechRecognition} and can easily become the next big thing.
+It could be also beneficial for older or disabled users~\cite{SpeechRecognition} and can easily become the next big thing.
 
@@
 So what we should do about it?
-We can create reuseable components and conditionaly load resources.
+We can create reusable components and conditionally load resources.
 Web components allow us to use custom HTML elements in the browser.
@@
 
-We have detected several web componenets and input methods and tried to verify which of them provide better experience for the website users and are also useful for the web developers.
+We have detected several web components and input methods and tried to verify which of them provide better experience for the website users and are also useful for the web developers.
 There have been made series of experiments on both adaptive input methods and adaptive web components.
@@
 Speech input provides a great opportunity to take a complete control over web application using only voice commands.
-For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reuseable module.
+For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reusable module.
 Speech recognition is however currently possible online only.
@@
 These configurations are bound to utterance watchers and the callback is called when voice command is recognised.
-Regular expressions are benefitial since we can set up a single watcher for dynamical commands where one command can be used for multiple subjects.
+Regular expressions are beneficial since we can set up a single watcher for dynamical commands where one command can be used for multiple subjects.
 
@@
 One of the biggest problems of the voice commands is however incorrect speech recognition.
-To solve this issue we can conditionalize regular expressions or use uterance error correction.
+To solve this issue we can conditionalize regular expressions or use utterance error correction.
 
@@
 We remember starting device orientation and compare it to the current one.
-Based on this substraction we can make a decision which direction we scroll and how fast.
+Based on this subtraction we can make a decision which direction we scroll and how fast.
 The bigger the orientation difference is, the faster we scroll.
@@
 
-We use the Mobile First principe so we make a default elemet static and pull in a static image.
+We use the Mobile First principe so we make a default element static and pull in a static image.
 This approach saves a lot of web traffic and becasue of limited mobile internet plans also user's money.
@@
 Adaptive web components are a great to save an unwonted web traffic.
-They also icrease user experience because the web page produces less requests and loads faster.
+They also increase user experience because the web page produces less requests and loads faster.
 However the limitations also exist because many websites need custom elements and design.

### 2014-03-15 paper/paper.tex
style: reformulated phrases

@@
 
-There is no one true input for the Web. We have to contend with fingers, mice, keyboards, voice and more. The challenge for us over the next few years is not designing for one input but many.
+There is no universal input for the Web. We have to contend with fingers, mice, keyboards, voice and more. The challenge for us over the next few years is not designing for one input but many.
 
@@
 
-Touch is no longer just isolated to smartphones and tablets. Many big screens in laptops or desktops nowadays are touch capable. Every desktop design has to be touch-friendly now.
+Touch is no longer just isolated to smartphones and tablets. Nowadays many large screens on laptops or desktops are touch capable. Thus every desktop design has to be touch-friendly now.
 
@@
 One of the most common critiques against responsive Web design is that Web sites have large file size and so they are slowing Web pages down.
-But we can make responsive sites perform well, we just have to the work to make it possible~\cite{20mb}.
+But we can make responsive sites perform well, we just have to do the work to make it possible~\cite{20mb}.
 
@@
 Latency is a much bigger fragment to download times.
-LTE reduces tower latency by several milliseconds but we still need to make a number of connections to download data to our devices~\cite{performancebrowsernetworking}.
+LTE standart reduces tower latency by several milliseconds but we still need to make a number of connections to download data to our devices~\cite{performancebrowsernetworking}.
 
@@
 
-But there are many more interesting things we can achieve using speech input.
+But there are much more interesting things we can achieve using speech input.
 We can even use multiple languages for speech recognition.
@@
 
-We have access to 3 axis rotation informations which are recalculated every time on device orientation change.
+We have access to 3 axis rotation information which are recalculated every time on device orientation change.
 We remember starting device orientation and compare it to the current one.
@@
 We use a video camera stream and devide it into image frames.
-Then we can detect a website user in the each frame using a hsv filter.
+Then we can detect a website user in the each frame using a HSV filter.
 When we compare all pixels in two adjacent frames we get difference points.
@@
 However we need a proper ambient lighting.
-There can be detection issues in too dark and too light scenes.
+There can be detection issues in too dark and too bright scenes.
 
@@
 
-There are a lot of commonly used web services that produce unnecessary traffic.
+There are many commonly used web services that produce unnecessary traffic.
 Elements like videos or maps are a common part of the most web sites.
-All of them produces many requests and the web traffic even the website user doesn't want to watch the video or browse the map.
+All of them produces many requests and the web traffic so the website user doesn't want to watch the video or browse the map.
 There are also native mobile application for that services with better perfomance which provide full user experience.
@@
 We use the Mobile First principe so we make a default element static and pull in a static image.
-This approach saves a lot of web traffic and becasue of limited mobile internet plans also user's money.
+This approach saves a lot of web traffic and becasue of limited mobile data plans also user's money.
 We can then detect when it's appropriate to download the embedded map or to launch the native mobile application.
@@
 As we have expected, the most popular input method is speech input since we can control an entire web application using only voice commands.
-Gyroscope and video motion are also useful input methods, but there are limited occasions where to use them and can be used as supplementary input method only.
+Gyroscope and video motion are also useful input methods, but there are limited possibilities where to use them and can be used as supplementary input method only.
 All of them however provide a great opportunity to enhance user experience.
 
-Adaptive web components are a great to save an unwonted web traffic.
+Adaptive web components are a great to save an unwanted web traffic.
 They also increase user experience because the web page produces less requests and loads faster.
@@
 More changes are coming, new devices, web APIs and beyond.
-What will it look like in a couple of years?
+How it will look in a few years?
 The devices will be more diversified and have the web access.

### 2014-03-16 paper/paper.tex
fix: remove contractions

@@
 The basic approach how to provide an optimal viewing experience is to use ``Responsive web design'' which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
-While creating flexible layouts is important, there's a lot more that requires remarkable adaptive web experiences.
+While creating flexible layouts is important, there is a lot more that requires remarkable adaptive web experiences.
 The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.
@@
 The power of the web is its ubiquity.
-No one knows what the landscape is going to appear in a couple years, but there's a reasonable probability the new devices in a few years from now will have access to the web.
+No one knows what the landscape is going to appear in a couple years, but there is a reasonable probability the new devices in a few years from now will have access to the web.
 Because of this, we need to preserve and embrace the web's ubiquity.
 This requires us to provide full web experiences regardless of how and where people access the web.
-It's important to remain in creating flexible interfaces that can adapt to any screen size.
+It is important to remain in creating flexible interfaces that can adapt to any screen size.
 Performance is often less important to everything else.
@@
 
-Adaptive web design is fundamentally progressive enhancement, but it's being applied to a much larger and more diverse landscape.
+Adaptive web design is fundamentally progressive enhancement, but it is being applied to a much larger and more diverse landscape.
 We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
@@
 Creating flexible layouts is important, but there are many more factors we need to think about.
-It's also important to consider as well ergonomics, touch capability, other input methods, internet connections and many other features that can be detected.
+It is also important to consider as well ergonomics, touch capability, other input methods, internet connections and many other features that can be detected.
 
@@
 The current Google Glass interface is limited to a floating display above head.
-We don't have full range of motion and, as a result, no spatial cues or depth in the interface.
+We do not have full range of motion and, as a result, no spatial cues or depth in the interface.
 
@@
 So 7mm should be 30pixels~\cite{designingfortouch}.
-However, things aren't so easy because of dynamic viewports.
+However, things are not so easy because of dynamic viewports.
 It means that input elemtents in website have to be usually bigger.
@@
 We can now use speech recognition to take a full control of the web site as we have access to continuous recognition stream.
-We don't need another input methods at all.
+We do not need another input methods at all.
 A speech feedback for user interaction is also important and we can use speech synthesis feature for it.
@@
 From controlling the user interface based on three dimensional motion as input, to combining device motion with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}.
-There's a lot of interesting interface designs made possible by Device Motion.
+There is a lot of interesting interface designs made possible by Device Motion.
 It depends on us how we use them.
@@
 We can build web games and another real time interfaces.
-There's again a lot of interesting interface designs made possible.
+There is again a lot of interesting interface designs made possible.
 
@@
 We all should be interested in page speed and mobile performance because people need fast experiences on the Web.
-There's lot of studies that highlight the importance of speed.
-More than half of people with a bad loading experience on mobile, won't come back~\cite{performancebrowsernetworking}.
-73\% of mobile internet users say they've encountered Web pages that are too slow, a 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
+There is lot of studies that highlight the importance of speed.
+More than half of people with a bad loading experience on mobile, will not come back~\cite{performancebrowsernetworking}.
+73\% of mobile internet users say they have encountered Web pages that are too slow, a 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
 Speed is an esencial part of our strategy and we should care about it.
@@
 There are many different types of internet connections.
-Mobile network speeds have rose but this doesn't help much as page load times are still high as bandwidth increases.
+Mobile network speeds have rose but this does not help much as page load times are still high as bandwidth increases.
 Latency is a much bigger fragment to download times.
@@
 
-However some problems have been detected. The biggest one is that browser vendors don't use specification correctly and use own orientation ranges and directions. This causes some scroll issues.
+However some problems have been detected. The biggest one is that browser vendors do not use specification correctly and use own orientation ranges and directions. This causes some scroll issues.
 
@@
 Elements like videos or maps are a common part of the most web sites.
-All of them produces many requests and the web traffic so the website user doesn't want to watch the video or browse the map.
+All of them produces many requests and the web traffic so the website user does not want to watch the video or browse the map.
 There are also native mobile application for that services with better perfomance which provide full user experience.
@@
 This approach saves a lot of web traffic and becasue of limited mobile data plans also user's money.
-We can then detect when it's appropriate to download the embedded map or to launch the native mobile application.
+We can then detect when it is appropriate to download the embedded map or to launch the native mobile application.
 
@@
 If the native experience is unavailable, the user is redirected to the service website, where they receive a full-screen experience.
-However, we don't always want to open the native application.
+However, we do not always want to open the native application.
 We can download an embedded map or play the video directly after the tap.

### 2014-03-16 paper/paper.tex
fix: motion detected by gyroscope rotation and camera

@@
 
-\subsubsection*{Video Motion} % (fold)
+\subsubsection*{Video motion detection} % (fold)
 \label{sub:video_motion}
@@
 Adaptive input methods provide alternative way of web application control and extend current approach.
-We have been experimenting to control web applications using voice commands, gyroscope motion and video motion.
+We have been experimenting to control web applications using voice commands, motion detected by a gyroscope or a camera.
 
@@
 
-We have used device orientation API as alternative control method to web application and built a module which can scroll in website using gyroscope rotation.
+We have used device orientation API as alternative control method to web application and built a module which can scroll in website detecting rotation using a gyroscope.
 Developers can use this module as replacement of the global application scroll instead of touch events or mice wheel and also a local element scroll too.
@@
 
-\subsubsection{Video camera motion} % (fold)
+\subsubsection{Video motion detection} % (fold)
 \label{ssub:video_camera_motion}
@@
 We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom.
-Using video camera motion we can enhance experience in websites and games.
+Using video motion detection we can enhance experience in websites and games.
 However we need a proper ambient lighting.

### 2014-03-16 paper/paper.tex
style: normal first paragraphs after figures

@@
 
-However some problems have been detected. The biggest one is that browser vendors do not use specification correctly and use own orientation ranges and directions. This causes some scroll issues.
+\noindent However some problems have been detected.
+The biggest one is that browser vendors do not use specification correctly and use own orientation ranges and directions.
+This causes some scroll issues.
 
@@
 
-We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom.
+\noindent We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom.
 Using video motion detection we can enhance experience in websites and games.
@@
 
-By default we set an anchor to the location of the service website.
+\noindent By default we set an anchor to the location of the service website.
 When a user taps the component, the browser will try to open the native application where they can have a better experience.

### 2014-03-16 paper/paper.tex
refactor: restyle sentences

@@
 Several new methods for designing web are rapidly evolving.
-We present a new way of web components adaptation based on a device features and external conditions in our work and new possibilities of interaction with web application based on speech recognition, motion or device rotation.
+We present a new way of web components adaptation based on a device features and external conditions in our work.
+We introduce new possibilities of interaction with the web applications based on speech recognition, motion or device rotation.
 \end{abstract}
@@
 
-We consider ``adaptive web design'' as an equal with creating a single Web experience that adjusts based on the capabilities of the device and browser.
+We consider ``adaptive web design'' as an equal with creating a single Web experience.
+We can adjust it based on the capabilities of the device and browser.
 Website can access sensors in devices and use them to enhance user experience.
@@
 
-The best touch interface is sometimes no touch at all. We can use sensors and speech input which is the next frontier for interaction design.
+The best interface can be sometimes controlled without touching at all. We can use sensors and speech input which is the next frontier for interaction design.
 
@@
 
-From controlling the user interface based on three dimensional motion as input, to combining device motion with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}.
-There is a lot of interesting interface designs made possible by Device Motion.
+We can control the user interface based on three dimensional motion as input or we can combine it with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}.
+There are a lot of interesting interface designs made possible by device motion.
 It depends on us how we use them.
@@
 However, more interactive elements require additional consideration.
-Even then use of an embedded elements directly still might not make sense because of unnecessary traffic, while adaptive techniques reduces it.
-We can still replace basic static image with richer elements.
+Even then use of an embedded elements directly still might not make sense because of unnecessary traffic.
+We can still use adaptive techniques to reduce it and replace basic static image with richer elements.
 

### 2014-03-16 paper/paper.tex
feat: reveal the attendance
feat: add tested web components

@@
 We have also received a lot of feedback from the community which helped us to verify the proposed concept.
+According to analytics the experiment has been attended by thousands of users and still has the weekly traffic one hundred of unique visitors.
 
@@
 
-We use the Mobile First principe so we make a default element static and pull in a static image.
+We have used the Mobile First principle to develop Google Maps and Youtube videos web components.
+So we make a default element static and pull in a static image.
 This approach saves a lot of web traffic and becasue of limited mobile data plans also user's money.

### 2014-03-17 paper/paper.tex
feat: experiment using voice commands

@@
 For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reusable module.
-Speech recognition is however currently possible online only.
+Speech recognition is however currently an experimental feauture and is possible online only.
 
@@
 
+We have created an experiment based on our module which provides control over to-do list.
+There were 7 voice commands using exact expressions and 9 using regular expressions.
 But there are much more interesting things we can achieve using speech input.

### 2014-03-17 paper/paper.tex
feat: add saved traffic and page load times
feat: video motion detection experiment

@@
 \noindent We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom.
+The experiment has been attended by hundreds of users.
 Using video motion detection we can enhance experience in websites and games.
-However we need a proper ambient lighting.
+We can also detect device motion and orientation changes so it can be used as a supplementary input method to the accelerometer and gyroscope rotation.
+However we cannot take a full control over the webapp and need a proper ambient lighting.
 There can be detection issues in too dark and too bright scenes.
@@
 
+Using adaptive web components we reduce initial traffic by 400 kB and a page load time by 350 ms for a youtube video in the average.
+For the map elemets the amount of saved traffic and load times are various and depend on element size.
 This approach works quite well for simple use cases.

### 2014-03-18 paper/paper.tex
feat: gyroscope rotation experiment
feat: voice commands experiment
refactor: google glass description

@@
 We also have wearable computers.
-The current Google Glass interface is limited to a floating display above head.
-We do not have full range of motion and, as a result, no spatial cues or depth in the interface.
+The current Google Glass interface is also limited to several input methods.
 
@@
 There were 7 voice commands using exact expressions and 9 using regular expressions.
+This has been the most popular input method and the experiment has been attended by thousands of users.
 But there are much more interesting things we can achieve using speech input.
@@
 
-\noindent However some problems have been detected.
+\noindent The experiment has been attended by thousands of users.
+However some problems have been detected.
 The biggest one is that browser vendors do not use specification correctly and use own orientation ranges and directions.

### 2014-03-18 paper/paper.tex
fix: typos

@@
 
-Almost every moder device contains a video camera.
+Almost every modern device contains a video camera.
 This is a great opportunity to introduce video motion to web applications.
@@
 Elements like videos or maps are a common part of the most web sites.
-All of them produces many requests and the web traffic so the website user does not want to watch the video or browse the map.
+All of them produce many requests and the web traffic so the website user does not want to watch the video or browse the map.
 There are also native mobile application for that services with better perfomance which provide full user experience.

### 2014-03-18 extended-abstract/extended-abstract.tex
feat: create extended abstract

--- 2014-03-18 paper/paper.tex
@@
 \documentclass{iitsrc}
-\usepackage{graphicx}
-\usepackage{mflogo}
-\usepackage{url}
-\usepackage[utf8]{inputenc}%some compilers use utf8x and need the prerendredUnicode characters
-%\PrerenderUnicode{áäčďéíľĺňóôŕšťúýžÁÄČĎÉÍĽĹŇÓÔŔŠŤÚÝŽ}
+\usepackage[utf8]{inputenc}
 
-% Please do not remove the following commands:
-\editpages{1}{6}
-\hyphenation{pha-blets}
+% Please do not remove the following command:
+\editpages{1}{2}
 
@@
 
-\begin{abstract}
-Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also high-latency networks.
-But there are not just smartphones and desktop computers.
-We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
-So it is necessary to adapt web pages for different devices and new interaction methods.
-Several new methods for designing web are rapidly evolving.
-We present a new way of web components adaptation based on a device features and external conditions in our work.
-We introduce new possibilities of interaction with the web applications based on speech recognition, motion or device rotation.
-\end{abstract}
-
-\section{Introduction}
+\section*{Extended Abstract}
 
@@
 Even for the average web site things have changed a lot over four years: browser share, operating systems, screen resolutions, and more~\cite{ui17}.
-
 The basic approach how to provide an optimal viewing experience is to use ``Responsive web design'' which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
@@
 
-The power of the web is its ubiquity.
-No one knows what the landscape is going to appear in a couple years, but there is a reasonable probability the new devices in a few years from now will have access to the web.
-Because of this, we need to preserve and embrace the web's ubiquity.
-This requires us to provide full web experiences regardless of how and where people access the web.
-It is important to remain in creating flexible interfaces that can adapt to any screen size.
-Performance is often less important to everything else.
-``Progressive enhancement'', feature detection and many other techniques allow us to increase experience that allow us to support more devices while still optimizing for the finest.
-The key aspect of ``Future Friendly'' thinking is to acknowledge and embrace unpredictability.
-Nobody knows where things are going but the one thing we can trust is the evolution.
-
-Adaptive web design is fundamentally progressive enhancement, but it is being applied to a much larger and more diverse landscape.
+Adaptive web design is fundamentally ``progressive enhancement'', but it is being applied to a much larger and more diverse landscape.
 We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
@@
 
-\section{Adaptive Input methods}
+% Experiments
 
-As we have many types of devices with web access we also have to adapt input methods for them.
-It is not just about screen sizes, but many displays also have touch capabilities, are equiped with microphone, accelerometer, gyroscope or camera.
-
-Web browsers on TVs are actually really good but the input is terrible so no one uses them.
-Input is much more important to interface design than screen size.
-The input defines what a design needs to do in order to accomplish a task~\cite{adaptiveinput}.
-We also have wearable computers.
-The current Google Glass interface is also limited to several input methods.
-
-There is no universal input for the Web. We have to contend with fingers, mice, keyboards, voice and more. The challenge for us over the next few years is not designing for one input but many.
-
-\subsubsection*{Touch} % (fold)
-\label{sub:touch}
-
-Touch is no longer just isolated to smartphones and tablets. Nowadays many large screens on laptops or desktops are touch capable. Thus every desktop design has to be touch-friendly now.
-
-The optimal touch target size is 7mm, based on the average size of human finger tips and pads.
-CSS2.1 defines a pixel as 1/96 of an inch.
-So 7mm should be 30pixels~\cite{designingfortouch}.
-However, things are not so easy because of dynamic viewports.
-It means that input elemtents in website have to be usually bigger.
-
-The best interface can be sometimes controlled without touching at all. We can use sensors and speech input which is the next frontier for interaction design.
-
-% subsubsection touch (end)
-
-\subsubsection*{Speech} % (fold)
-\label{sub:speech}
-
-The speech input aims to provide an alternative input method for web applications, without using a keyboard or other physical device.
-This is no longer science fiction but reality.
-Many companies rely on it and deploy it to the modern devices and software.
-It could be also beneficial for older or disabled users~\cite{SpeechRecognition} and can easily become the next big thing.
-
-We can now use speech recognition to take a full control of the web site as we have access to continuous recognition stream.
-We do not need another input methods at all.
-A speech feedback for user interaction is also important and we can use speech synthesis feature for it.
-
-% subsubsection speech (end)
-
-\subsubsection*{Device motion} % (fold)
-\label{sub:device_motion}
-
-We can use a lot of sensors in the devices to detect the device motion.
-It is made possible by a combination of always-on sensors as are an accelerometer a gyroscope, and a magnetometer, that tell us a lot about how a device is moving through the space around it.
-The ability of these sensors to provide precise information about the movement of a device opens up new design possibilities for web applications~\cite{ultrabooks}.
-
-We can control the user interface based on three dimensional motion as input or we can combine it with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}.
-There are a lot of interesting interface designs made possible by device motion.
-It depends on us how we use them.
-
-% subsubsection device_motion (end)
-
-\subsubsection*{Video motion detection} % (fold)
-\label{sub:video_motion}
-
-Many modern devices contains built in video camera sensor which we can use as alternative method to device motion.
-We can access video stream and analyse landscape around the device.
-Video motion detection is a way of defining user activity in a scene by analyzing image data and differences in a series of images.
-
-We can detect user motion and use it as an alternatove part of input method.
-We can build web games and another real time interfaces.
-There is again a lot of interesting interface designs made possible.
-
-% subsubsection video_motion (end)
-
-\section{Adaptive Web Components} % (fold)
-\label{sec:adaptive_web_components}
-
-One of the most common critiques against responsive Web design is that Web sites have large file size and so they are slowing Web pages down.
-But we can make responsive sites perform well, we just have to do the work to make it possible~\cite{20mb}.
-
-We all should be interested in page speed and mobile performance because people need fast experiences on the Web.
-There is lot of studies that highlight the importance of speed.
-More than half of people with a bad loading experience on mobile, will not come back~\cite{performancebrowsernetworking}.
-73\% of mobile internet users say they have encountered Web pages that are too slow, a 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
-Speed is an esencial part of our strategy and we should care about it.
-We can quantify its impact on the metrics and track it.
-
-There are many different types of internet connections.
-Mobile network speeds have rose but this does not help much as page load times are still high as bandwidth increases.
-Latency is a much bigger fragment to download times.
-LTE standart reduces tower latency by several milliseconds but we still need to make a number of connections to download data to our devices~\cite{performancebrowsernetworking}.
-
-So what we should do about it?
-We can create reusable components and conditionally load resources.
-Web components allow us to use custom HTML elements in the browser.
-We can enclose a simple element or an entire application logic within an HTML element~\cite{webcomponents}.
-We can build Web applications in a reusable, commutable and encapuslated way.
-
-% section adaptive_web_components (end)
-
-\section{Evaluation and experiments} % (fold)
-\label{sec:evaluation_and_experiments}
-
-We have detected several web components and input methods and tried to verify which of them provide better experience for the website users and are also useful for the web developers.
+We have detected several web components~\cite{webcomponents} and input methods and tried to verify which of them provide better experience for the website users and are also useful for the web developers.
 There have been made series of experiments on both adaptive input methods and adaptive web components.
 To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects.
-All of them have been released as open source and are available on GitHub~\footnotemark.
-
-\footnotetext{The modules and components we used to verify the usefulness of the proposed concept are available on GitHub \url{https://github.com/angular-adaptive}}
 
@@
 
-\subsection{Input methods} % (fold)
-\label{sub:input_methods}
+% Input
 
@@
 
-\subsubsection*{Voice commands} % (fold)
-\label{ssub:voice_commands}
-
-Speech input provides a great opportunity to take a complete control over web application using only voice commands.
-For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reusable module.
-Speech recognition is however currently an experimental feauture and is possible online only.
-
-Using speech recognition we get an utterance string which can be compared to voice commands from our configuration.
-We use regular expressions for this purpose with attached callback methods.
-These configurations are bound to utterance watchers and the callback is called when voice command is recognised.
-Regular expressions are beneficial since we can set up a single watcher for dynamical commands where one command can be used for multiple subjects.
-
-We have created an experiment based on our module which provides control over to-do list.
+We have created an experiment based on our module which provides voice control over to-do list.
 There were 7 voice commands using exact expressions and 9 using regular expressions.
 This has been the most popular input method and the experiment has been attended by thousands of users.
-But there are much more interesting things we can achieve using speech input.
-We can even use multiple languages for speech recognition.
 One of the biggest problems of the voice commands is however incorrect speech recognition.
@@
 
-% subsubsection voice_commands (end)
-
-\subsubsection*{Gyroscope rotation} % (fold)
-\label{ssub:gyroscope_rotation}
-
-We have used device orientation API as alternative control method to web application and built a module which can scroll in website detecting rotation using a gyroscope.
-Developers can use this module as replacement of the global application scroll instead of touch events or mice wheel and also a local element scroll too.
-
-We have access to 3 axis rotation information which are recalculated every time on device orientation change.
-We remember starting device orientation and compare it to the current one.
-Based on this subtraction we can make a decision which direction we scroll and how fast.
-The bigger the orientation difference is, the faster we scroll.
-
-\begin{figure}[ht]
-    \begin{center}
-        \includegraphics[width=0.15\textwidth]{../images/gyroscope}
-        \caption{Scrolling in the webpage by gyroscope}
-        \label{fig:gyroscope}
-    \end{center}
-\end{figure}
-
-\noindent The experiment has been attended by thousands of users.
+The experiment based on gyroscope rotation which allows to scroll in the application has been attended by thousands of users.
 However some problems have been detected.
@@
 
-% subsubsection gyroscope_rotation (end)
-
-\subsubsection{Video motion detection} % (fold)
-\label{ssub:video_camera_motion}
-
 Almost every modern device contains a video camera.
@@
 We can control web sites using motion gestures.
-We use a video camera stream and devide it into image frames.
-Then we can detect a website user in the each frame using a HSV filter.
-When we compare all pixels in two adjacent frames we get difference points.
-When we apply this comparision to multiple frames we can calculate a motion vector.
-
-\begin{figure}[ht]
-    \begin{center}
-        \includegraphics[width=0.5\textwidth]{../images/videomotion}
-        \caption{Converting video stream into motion vector}
-        \label{fig:videomotion}
-    \end{center}
-\end{figure}
-
-\noindent We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom.
 The experiment has been attended by hundreds of users.
@@
 
-% subsubsection video_camera_motion (end)
+% Web Components
 
-% subsection input_methods (end)
-
-\subsection{Web Components} % (fold)
-\label{sub:web_components}
-
-There are many commonly used web services that produce unnecessary traffic.
-Elements like videos or maps are a common part of the most web sites.
-All of them produce many requests and the web traffic so the website user does not want to watch the video or browse the map.
+There are many commonly used web services that produce many requests and unnecessary trafficeven when the website user does not want to watch the video or browse the map.
+There is lot of studies that highlight the importance of speed.
+More than half of people with a bad loading experience on mobile, will not come back~\cite{performancebrowsernetworking}.
+73\% of mobile internet users say they have encountered Web pages that are too slow, a 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
 There are also native mobile application for that services with better perfomance which provide full user experience.
-So what can we to do?
 This is a great opportunity to utilize conditional loading to serve the best experience for the right context.
-
 We have used the Mobile First principle to develop Google Maps and Youtube videos web components.
-So we make a default element static and pull in a static image.
-This approach saves a lot of web traffic and becasue of limited mobile data plans also user's money.
-We can then detect when it is appropriate to download the embedded map or to launch the native mobile application.
-
-\begin{figure}[ht]
-    \begin{center}
-        \includegraphics[width=0.55\textwidth]{../images/maps.png}
-        \caption{Maps component}
-        \label{fig:maps}
-    \end{center}
-\end{figure}
-
-\noindent By default we set an anchor to the location of the service website.
-When a user taps the component, the browser will try to open the native application where they can have a better experience.
-If the native experience is unavailable, the user is redirected to the service website, where they receive a full-screen experience.
-However, we do not always want to open the native application.
-We can download an embedded map or play the video directly after the tap.
-The user can interact with them directly in the web application so developers have to make a decision between these choices.
-
 Using adaptive web components we reduce initial traffic by 400 kB and a page load time by 350 ms for a youtube video in the average.
@@
 
-% subsection web_components (end)
-
-% section evaluation_and_experiments (end)
-
-\section{Conclusion} % (fold)
-\label{sec:conclusion}
+% Conclusion
 
@@
 All of them however provide a great opportunity to enhance user experience.
-
 Adaptive web components are a great to save an unwanted web traffic.
@@
 
-% section conclusion (end)
-
 \bibliography{common}

### 2014-03-18 extended-abstract/extended-abstract.tex
refactor: truncate the extended abstract

@@
 Even for the average web site things have changed a lot over four years: browser share, operating systems, screen resolutions, and more~\cite{ui17}.
-The basic approach how to provide an optimal viewing experience is to use ``Responsive web design'' which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}.
+The basic approach how to provide an optimal viewing experience is to use ``Responsive web design''.
 While creating flexible layouts is important, there is a lot more that requires remarkable adaptive web experiences.
-The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.
 
@@
 We also have many types of internet networks with different speed, latency and quality.
-Responsive design is also one technique in an adaptive web design strategy.
-Creating flexible layouts is important, but there are many more factors we need to think about.
-It is also important to consider as well ergonomics, touch capability, other input methods, internet connections and many other features that can be detected.
-
+However there are many more factors we need to think about.
+It is also important to consider as well ergonomics, input methods, internet connections and many other features that can be detected.
 We consider ``adaptive web design'' as an equal with creating a single Web experience.
@@
 To prove the usefulness of the proposed concept we have designed and implemented several reusable modules and components and we have used them in propotype web projects.
-
 We have tracked amount of saved web traffic and web requests, webpage rendering time and interest in alternative input methods.
 We have also received a lot of feedback from the community which helped us to verify the proposed concept.
-According to analytics the experiment has been attended by thousands of users and still has the weekly traffic one hundred of unique visitors.
+The experiments has been attended by thousands of visitors.
 
@@
 Almost every modern device contains a video camera.
-This is a great opportunity to introduce video motion to web applications.
-We can control web sites using motion gestures.
-The experiment has been attended by hundreds of users.
+This is a great opportunity to control web sites using motion gestures.
+This experiment has been attended by hundreds of users.
 Using video motion detection we can enhance experience in websites and games.
@@
 More than half of people with a bad loading experience on mobile, will not come back~\cite{performancebrowsernetworking}.
-73\% of mobile internet users say they have encountered Web pages that are too slow, a 1 second delay can result in a 7\% reduction in conversions~\cite{pagespeed}.
+73\% of mobile internet users say they have encountered Web pages that are too slow~\cite{pagespeed}.
 There are also native mobile application for that services with better perfomance which provide full user experience.
@@
 As we have expected, the most popular input method is speech input since we can control an entire web application using only voice commands.
-Gyroscope and video motion are also useful input methods, but there are limited possibilities where to use them and can be used as supplementary input method only.
+Gyroscope and video motion detection are also useful input methods, but there are limited possibilities where to use them and can be used as supplementary input method only.
 All of them however provide a great opportunity to enhance user experience.
@@
 
-More changes are coming, new devices, web APIs and beyond.
-How it will look in a few years?
-The devices will be more diversified and have the web access.
-So we have to prepare the Web to this evolution and provide the best user experience, design for many inputs and save the inessential web traffic.
+More changes are coming. So we have to prepare the Web to this evolution and provide the best user experience, design for many inputs and save the inessential web traffic.
 

### 2014-03-18 extended-abstract/extended-abstract.tex
fix: typos

@@
 
-Adaptive web design is fundamentally ``progressive enhancement'', but it is being applied to a much larger and more diverse landscape.
+Adaptive web design is fundamentally ``Progressive enhancement'', but it is being applied to a much larger and more diverse landscape.
 We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more.
@@
 However there are many more factors we need to think about.
-It is also important to consider as well ergonomics, input methods, internet connections and many other features that can be detected.
+It is also important to consider as well ergonomics, input methods, internet connections and other features that can be detected.
 We consider ``adaptive web design'' as an equal with creating a single Web experience.
@@
 We have also received a lot of feedback from the community which helped us to verify the proposed concept.
-The experiments has been attended by thousands of visitors.
+The experiments have been attended by thousands of visitors.
 
@@
 Adaptive input methods provide alternative way of web application control and extend current approach.
-We have been experimenting to control web applications using voice commands, motion detected by a gyroscope or a camera.
+We have been experimenting to control web applications using voice commands, motion detected by a gyroscope and a video camera.
 
@@
 
-The experiment based on gyroscope rotation which allows to scroll in the application has been attended by thousands of users.
+The another experiment based on gyroscope rotation which allows to scroll in the application has been attended by thousands of users.
 However some problems have been detected.
@@
 We can also detect device motion and orientation changes so it can be used as a supplementary input method to the accelerometer and gyroscope rotation.
-However we cannot take a full control over the webapp and need a proper ambient lighting.
+However we cannot take a full control over the web app and need a proper ambient lighting.
 There can be detection issues in too dark and too bright scenes.
@@
 
-There are many commonly used web services that produce many requests and unnecessary trafficeven when the website user does not want to watch the video or browse the map.
+There are many commonly used web services that produce many requests and unnecessary traffic even when the website user does not want to use them.
 There is lot of studies that highlight the importance of speed.
@@
 We have used the Mobile First principle to develop Google Maps and Youtube videos web components.
-Using adaptive web components we reduce initial traffic by 400 kB and a page load time by 350 ms for a youtube video in the average.
-For the map elemets the amount of saved traffic and load times are various and depend on element size.
+Using adaptive web components we reduce initial traffic by 400 kB and a page load times by 350 ms for a youtube video in the average.
+The amount of saved traffic and load times are various for the map elemets and depend on element size.
 This approach works quite well for simple use cases.
@@
 However the limitations also exist because many websites need custom elements and design.
-As a result the adaptive web components produce less interest than adaptive input methods, but are the necessary part of the Web.
+As a result the adaptive web components produce less interest than adaptive input methods.
 
